Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-26 demystify.tex
updates

\paragraph{Interviews} Just like a job application, you likely will get interviews from schools. The most common case is that a prof. is interested in working with you and wants to chat to make a decision, e.g., to offer RA (\autoref{sec:ra})). In some cases, the interview is done by several professors, e.g., to see if a student fits in their group or to recruit a very strong student to their program. The interview can also be done by adcom members to see if the student fits their program.
%The professor might include one of their current students as part of the interview.

@@

\paragraph{Timeline} The timeline for interviews and notification letters varies.  Faculty set up interviews based on their (busy) schedule. Do not be surprised if you get an interview invitation at the last minute. Some schools do not do interviews at all.

>>>>

\subsection{Interviews}

Just like a job application, you likely will get interviews from schools. The most common case is that a prof. is interested in working with you and wants to chat to make a decision, e.g., to offer RA (\autoref{sec:ra}). In some cases, the interview is done by several professors, e.g., to see if a student fits in their group or to recruit a very strong student to their program. The interview can also be done by adcom members to see if the student fits their program.
%The professor might include one of their current students as part of the interview.

@@

\subsection{Timeline}

The timeline for interviews and notification letters varies.  Faculty set up interviews based on their (busy) schedule. Do not be surprised if you get an interview invitation at the last minute. Some schools do not do interviews at all.
